\Title

### 2023-02-09 Grimaldi-etal-BiolCybernetics.tex
Methods : A

%: fig:motion_task
    \includegraphics[width=0.95\linewidth]{figures/motion_task.pdf}
        {\bf - Motion Detection Task.} {\bf (left)}~We use large natural images ($512\times512$) in which an aperture ($128\times128$) extracts a cropped image around the view axis. To mimic the effect of a saccadic eye movement, the view axis moves according to a stepwise random walk. We show an example path of the trajectory for $200$ time steps (green line). {\bf (right)}~Snapshot of the synthetic event stream at different time steps. The dynamics of the sub-image as a function of time produces a naturalistic movie. This can be transformed into an event-based representation. Mimicking the retina, this representation encodes proportional and pixel-wise increases or decreases in luminance in the image, i.e. ON (red) and OFF (blue) events. In the lower left corner of the images, the translation vector is shown in red. It is one of the possible classes of motion. Note the change in the direction of motion between the second and third image.}
    \label{fig:motion_task}
Once these eye trajectories are generated, we can apply them to a visual scene. For this purpose, we selected a database of 10 natural grayscale images that are commonly used to study the statistics of natural images~\citep{olshausen_emergence_1996}. Note that these have been pre-processed to equalize (i.e., whiten) the energy in each frequency band. This process is known to occur in the retino-thalamic pathway~\citep{dan_efficient_1996}. These images are $512 \times 512$ in size, and we will extract sub-images of size $128 \times 128$ positioned around the center of gaze at each time step. We will discretize time in $1~\ms$ bins and produce movies of duration $N_T = 250~\ms$. To avoid boundary effects, we will randomly position a plot of the full trajectory in image space so that the subimage is translated using the position given by the trajectory at each time step. The translation is computed using a coordinate roll in the horizontal and vertical dimensions, followed by a subpixel translation defined in Fourier space~\citep{perrinet_sparse_2015}. Note that the magnitude of the displacement is relative to the time bin, and we have defined the velocity to correspond to a movement of one pixel per frame (i.e., per time bin).

>>>>

%%%-----------------------------------------------------------------
%: fig:motion_task
%%%-----------------------------------------------------------------
\begin{figure}%[h!]%[ht!]
    \centering
    \includegraphics[width=0.95\linewidth]{figures/motion_task.pdf}
    \caption{
        {\bf - Motion Detection Task.} {\bf (Left)}~We use large natural images ($512\times512$) in which an aperture ($128\times128$) extracts a cropped image around the view axis. To mimic the effect of a saccadic eye movement, the view axis moves according to a stepwise random walk. We show an example path of the trajectory for $200$ time steps (green line). {\bf (Right)}~Snapshot of the synthetic event stream at different time steps. The dynamics of the sub-image as a function of time produces a naturalistic movie. This can be transformed into an event-based representation. Mimicking the retina, this representation encodes pixel-per-pixel proportional increases or decreases in luminance in the image, i.e. ON (red) and OFF (blue) events. In the lower left corner of the images, the translation vector is shown in red as one of the possible classes of motion. Note the change in the direction of motion between the second and third image.}
    \label{fig:motion_task}
\end{figure}
%%%-----------------------------------------------------------------
Once these eye trajectories are generated, we can apply them to a visual scene. For this purpose, we selected a database of 10 natural grayscale images that are commonly used to study the statistics of natural images~\citep{olshausen_emergence_1996}. Note that these have been pre-processed to equalize (i.e., whiten) the energy in each frequency band. This process is known to occur in the retino-thalamic pathway~\citep{dan_efficient_1996}. These images are $512 \times 512$ in size, and we will extract sub-images of size $128 \times 128$ positioned around the center of gaze at each time step. We will discretize time in $1~\ms$ bins and produce movies of duration $N_T = 250~\ms$. To avoid boundary effects, we will randomly position the full trajectory in image space such that the subimage is translated using the position given by the trajectory at each time step without touching the borders. The translation is computed using a coordinate roll in the horizontal and vertical dimensions, followed by a subpixel translation defined in Fourier space~\citep{perrinet_sparse_2015}. Note that the magnitude of the displacement is relative to the time bin, and we have defined the velocity to correspond to a movement of one pixel per frame (i.e., per time bin).
